Decentralized autonomous organization to manage a trust\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-05 paper/Paper.tex
clarification on minQuorumDivisor
Hiro Mant [7:01 AM] 
I don't get this sentence from the whitepaper:

Hiro Mant [7:06 AM] 
> The sum ΞDAO + Rtotal is equal to the amount of ether raised plus the rewards received.
(p.2) (edited)

[7:08] 
If the DAO already spent some Ether to earlier proposals, E_DAO will be smaller than E_raised.
Where am I wrong here?

Hiro Mant [10:32 AM] 
@griff: But two lines above the cited phrase, it says:

[10:32] 
>  ΞDAO is the amount of ether owned by the DAO

[10:33] 
So EDAO is not the total recived  (sale+rewards

[10:33] 
but income - spent

[10:33] 
?

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward token as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received.

>>>>

After $t_p$ has passed, any token holder can call a function in the DAO contract that will verify that the majority voted in favor of the proposal and that quorum was reached; the function will execute the proposal if this is the case. If this is not the case, the proposal will be closed. The minimum quorum represents the minimum number of tokens required for a vote to be valid, is denoted by $q_{min}$, and calculated as follows:
\begin{equation}
 q_{min} = \frac{T_{\text{total}}}{d} + \frac{\Xi_{\text{transfer}} \cdot T_{\text{total}}}{3 \cdot (\Xi_{DAO} + R_{\text{total}})}
 \label{minQuorum}
\end{equation}
Where $d$ is the \verb|minQuorumDivisor|. This parameter's default value is $5$, but it will double in the case the quorum has not been met for over a year.
$\Xi_{DAO}$ is the amount of ether owned by the DAO and $R_{\text{total}}$ is the total amount of reward tokens ever generated as explained in section \ref{RewardToken} (also see \verb|totalRewardToken| in \ref{app:DAO}). The sum $\Xi_{DAO} + R_{\text{total}}$ is equal to the amount of ether raised plus the rewards received or said another way, the total amount of ether the DAO has ever received.
